### 2017-10-21 paper/sections/6_results.tex
paper: draft 3 with merge scale
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

@@

To show the contention at the metadata server of this approach, we scale the
number of journal merge events, each hitting different directories
in the namespace, in FigureX. The size of each journal is 100K files, the
maximum recommended directory size for CephFS. We also plot the cost of RPCs
with and without journaling.

@@

>>>>

\begin{figure}[tb] \centering
\includegraphics[width=1.0\linewidth]{graphs/mergescale.png} \caption{
[\href{https://...}{source}] Use Case 3: performance of merging client journals
at the metadata server. Performance is better than RPCs because (1) there are
less messages on the network and (2) the consistency/durability code paths in
the metadata server are bypassed. Merges are serialized and read from the local
disk, so keeping client journals in memory or on SSD will improve the
performance of ``decoupled" even more.  \ref{fig:mergescale}.
\label{fig:mergescale-sync}}
\end{figure}

@@

To show the contention at the metadata server of this approach, we scale the
number of journal merge events, each hitting different directories in the
namespace, in Figure~\ref{fig:mergescale}. The size of each journal is 100K
files, the maximum recommended directory size for CephFS. We also plot the cost
of RPCs with and without journaling; recall from Figure~\ref{fig:overhead-c}
that the scalability that max number of clients that the default metadata
server could support with RPCs is 18.

@@

\subsection{Discussion}
\begin{itemize}
  \item Composable guarantees: applications control their performance (knobs you didn't have before)
  \item Hardware features: adding hardware in strategic places
  \item Performance Prediction: quantifies the cost of each mechanism
\end{itemize}
